Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-05 paper/paper.tex
[paper] added discussion  points regarding the implementation details

//TODO: discuss differences between Flink and Spark.

@@

@@

 //TODO: add comparison between spark and Flink approaches 
 \end{itemize}
\section{Performance Results}

>>>>

@@

\par In summary, Flink  handles  the parallel consumers of Kafka stream implicitly, while a multiple \texttt{DStream} must be created in Spark Streaming and union them to have parallel Kafka receivers. The Flink's streaming processing is stateful that means there is no need to manage the stream state as the case in Spark streaming. A sort action is required in Spark Streaming to preserve the correct  order of the position messages inside the state update function.

@@

 \par To sum up, the same differences between Flink and Spark Streaming regarding the state management and parallel  consumers of Kafka stream as was discussed in Section 3.2.1. Another key difference between them, is how  to provide the global data model (e.g., sectors) in a streaming workload. Spark Streaming offers the \texttt{Broadcast} feature to handle this issue in efficient way, while the global data model is manually provided  to the stream operations in Flink.
\section{Performance Results}
